% This file was written by Augusto Goulart on May, 13, 2025
% He dedicates it to the public domain through CC0 (https://creativecommons.org/public-domain/cc0/)
\documentclass[a4paper,11pt]{article}

\usepackage{fontspec}
%\setmainfont{TeX Gyre Termes}
\setmainfont{TeX Gyre Cursor}
\setsansfont{TeX Gyre Heros}
\setmonofont{TeX Gyre Cursor}

\usepackage[a4paper,
  lmargin=20mm,
  rmargin=20mm,
  marginpar=0mm,
  top=20mm,
  bottom=20mm]{geometry}

\usepackage{setspace}
\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}
  

\begin{document}

\pagestyle{fancy}
\fancyhead{}
\fancyhead[R]{MMXXV}
\fancyfoot{}
\fancyfoot[R]{\tiny{}(single page)}
\fancyfoot[L]{\tiny{}This text has been written by Augusto Goulart on the thirteenth day of May, twenty twenty-five;\\he dedicates it to the public domain by waiving all of his rights to the work.}

\begin{spacing}{0.8}%
  \centering\LARGE%
  \textsc{Commitment of Moratorium}\\
  \Large%
  on use, research, and development\\of anti-human technology
  \vspace{5mm}
\end{spacing}

\noindent%
We, as a society, are currently in a turning point in our history, from climate change to global fascism, we are faced with many threats, but one of the worst ailments that have haunted us has only risen up this century, however, it is the result of many years of apathy, a plague that was once a divine blessing; something that exploits the Human psyche to make them slaves of their own mind; something that breaks communities and makes individuals lonely; we call it technology, specifically, information technology. From social media exploiting children, shortening attention spans, and making in-person interactions less desiring; to artificial intelligence making kids illiterate, tearing critical thinking, and stealing intellectual and artistic property.

As a developer, engineer or scientist, one must defer to some level of ethical thinking, and if so, inaction is not acceptable; not when it is so clear that we have caused this problem to begin with. Therefore, these are the limitations to be placed on our own creations, for the benefit of our communities, children and family:

\begin{enumerate}
  \item No machine shall speak to the Human, unless spoken to -- the Human tongue should not be given to the metal, words may only be announced by a machine in monotone. Likewise, no machine shall listen to the air waves or behold the light unless commanded by the Human.
  \item No machine shall usurp the physiognomy of the Human -- the metal should not resemble the flesh of the Human, for it cannot be the host of life that the Human houses in their divine shell.
  \item No machine shall mimic the Human emotion -- such a foul action should be met with utter disgust and open antagonism. Moreover, no machine shall take the Human place in community, the metal cannot befriend, raise, or council the Human.
  \item No machine shall be made for nothing -- the metal has been cast to be owned; it is a tool to be used by the Human; it must solve a problem to justify its existence.
  \item No machine shall lead the Human -- the metal only knows metal, it does not see beings; it does not see communities; to be Human is to sin; to be Human is to suffer; to lead, one must be able to see beyond the statistical veil.
  \item No machine shall produce the arts -- the metal is only able to copy; it cannot create; it only knows what is, not what can be; it should not take the Human thought as its own.
  \item The Human, whose intent is to elevate the metal to meet flesh, shall not be honored in society -- such a shameful act should be met with social dishonor and distrust.
\end{enumerate}

I, hereby, commit myself to adhere to these tenets to the best of my ability. I will share and advocate for this moratorium because I believe that our creations have formed an existential threat to Humanity, just as climate change has done, it is my duty to not repeat the errs of those who came before me. To every Human, peace and prosperity!

\end{document}
